Figures for Paper

### 2021-08-13 paper_figures.Rmd
Add NYGC IR plots

rel_rna_cryptic_amount %>%
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "UNC13A",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) +
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("UNC13A") +
    xlab("") +
    theme(legend.position = "none") +
    guides(color = FALSE) +
    theme(text = element_text(size = 20,family = 'sans'),
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28)) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(data = text_table[gene_name == "UNC13A"],aes(x = source, y= 1.35,label = padj_plot),size = 8) +
    geom_text(data = text_table[gene_name == "UNC13A"],aes(x = source, y= 1.2,label = log2FoldChange_plot),size = 8)

@@

rel_rna_cryptic_amount %>%
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "TARDBP",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) +
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("TARDBP") +
    xlab("") +
    theme(legend.position = "none") +
    guides(color = FALSE) +
    theme(text = element_text(size = 20,family = 'sans'),
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28)) +
    scale_y_continuous(labels = scales::percent,expand = expansion(mult = c(0, .1))) +
    geom_text(data = text_table[gene_name == "TARDBP"],aes(x = source, y= 1.35,label = padj_plot),size = 8) +
    geom_text(data = text_table[gene_name == "TARDBP"],aes(x = source, y= 1.2,label = log2FoldChange_plot),size = 8)

@@

```{r}
clean_data_table = fread(file.path(here::here(),"data","nygc_junction_information.csv"))
clean_data_table = clean_data_table %>%
    mutate(rs12973192 = fct_relevel(rs12973192,
                                    "C/C", "C/G", "G/G")) %>%
    mutate(number_g_alleles = as.numeric(rs12973192) - 1) %>%
    mutate(unc13a_cryptic_leaf_psi = ifelse(is.na(unc13a_cryptic_leaf_psi),0,unc13a_cryptic_leaf_psi)) %>%
    mutate(junction_reads_stmn2 = STMN2_annotated_leaf + STMN2_cryptic_leaf) %>%
    mutate(junction_reads_unc13a = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf + UNC13A_annotated_leaf) %>%
    unique()

@@

## Read length affects detection probability in cases

```{r readlength_detection_in_cases}
# library size 
#llumina HiSeq 2500 (125 bp paired end) or an Illumina NovaSeq (100 bp paired end). 
case_control_sequencing <- clean_data_table %>%
  filter(tissue_clean %in% c("Frontal_Cortex", 
                             "Lumbar_Spinal_Cord", 
                             "Cervical_Spinal_Cord", 
                             "Motor_Cortex", 
                             "Temporal_Cortex",
                             "Cerebellum")) %>% 
  filter(sequencing_platform != "")

quick_chiq = function(tbl){

    if(length(unique(tbl$sequencing_platform)) < 2){
      return(NA)
    }
    comparison_table = table(disease = tbl$disease_group2, 
                             sequencing_platform = tbl$sequencing_platform)
    print(comparison_table)

    p_value = chisq.test(comparison_table) %>%  broom::tidy() %>% pull(p.value)

    print(p_value)

case_control_sequencing %>% 
  group_by(tissue_clean) %>% 
  nest()  %>% 
  mutate(chiq_pvalue = map_dbl(data, quick_chiq))

@@

unc13a_sequencing_platform_pct %>%
  ggplot(aes(x = plot_name, y = detection )) + 
  geom_col(fill = "firebrick") +
  labs(title = "UNC13A CE detection and sequencing platform", 
       y = "UNC13A CE detected",x = element_blank(), subtitle = "Fisher exact test") + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free_x') +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_text(aes(x = 1.5, y = 1.05, label = paste0("p = ", signif(fisher_pvalue,digits = 2) ) )) +
  theme(legend.text = element_text(size = 15)) +
  ggpubr::theme_pubr()
 # scale_y_continuous(expand = c(0,0) ) 
```
## Effect of library size on CE discovery

```{r unc detection by library size  }
# library size 
force_colors = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
names(force_colors) = c("Control","ALS \n non-TDP","ALS-TDP","FTLD \n non-TDP","FTLD-TDP")

@@

## Effect of RIN and UNC13A discovery

```{r rin discovery}
force_colors = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
names(force_colors) = c("Control","ALS \n non-TDP","ALS-TDP","FTLD \n non-TDP","FTLD-TDP")

@@

@@

cell_types %>% 
  left_join(clean_data_table[,.(sample,
                               UNC13A_3prime_leaf,
                               UNC13A_5prime_1_leaf,
                               disease_group2,
                               disease_tissue)], by = 'sample') %>%
  filter(disease_group2 %in% c("FTLD-TDP", "ALS-TDP")) %>%
  filter(disease_tissue == T) %>% 
  filter(tissue_clean != "Thoracic_Spinal_Cord") %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  add_count(disease_group2,tissue_clean) %>% 
  mutate(n = n / 5) %>% 
  mutate(plot_name = glue::glue("{disease_group2} \n {n}")) %>% 
  filter(!is.na(inclusion_reads)) %>% 
  unique() %>% 
  ggplot(aes(x = cell, y = deconv, fill = unc13a_detected)) + 
  geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+
  geom_boxplot(outlier.color = NA) + 
  facet_wrap(~plot_name+tissue_clean,scales = 'free') +
  ggpubr::stat_compare_means(label = "p.signif") +
  ggpubr::stat_compare_means(label = "p.format",vjust = 1.2) +
  labs(title = "Cell type decomposition and UNC13A CE detection ",subtitle = "Wilcox test") + 
  ggpubr::theme_pubr()

@@

@@

```{r}
clean_data_table %>%
  filter(disease_tissue == T) %>%
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>%
  filter(junction_reads_stmn2 >= 30) %>%
  filter(junction_reads_unc13a >= 30) %>%
  # filter(UNC13A_3prime_leaf + UNC13A_5prime_1_leaf >= 2) %>%
  # filter(STMN2_cryptic_leaf >= 2) %>%
  filter(grepl("Cortex",tissue_clean)) %>%
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>%
  filter(unc13a_cryptic_leaf_psi > 0) %>%
  ggplot(aes(x = stmn_2_cryptic_psi_leaf, y = unc13a_cryptic_leaf_psi)) +
  geom_point() +
  stat_cor(size = 8,method = "spearman",cor.coef.name = "rho") +
  geom_smooth(method = lm, se = FALSE,color = "black") +
  xlab("STMN2 Cryptic PSI") +
  ylab("UNC13A CE PSI") +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 18)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L))  +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L))
```
## Scatter plot showing the correlation in non-log space RAP1GAP1 & STMN2 CE

@@

@@

overall_fisher %>%
  mutate(n_sample = n_non_detected + n_sample_detected) %>%
  mutate(detection_rate = n_sample_detected / n_sample) %>%
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>%
  ggplot(aes(x = detection_name, y = detection_rate, fill = detection_name)) +
  geom_col(show.legend = F) +
  ggpubr::theme_pubr() +
  scale_y_continuous(labels = scales::percent) +
  ylab("% of TDP-43 Proteionopathy Patients \n UNC13A Cryptic Detected") +
  theme(text = element_text(size = 18)) +
  xlab("N individuals") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739"))

@@

cowplot::plot_grid(rap1_fold_plot,pfkp_fold_plot)
```
# Nanopore

@@

p2_shsy <- ggplot(df %>% filter(classification != "",
                                type=="SHSY5Y"), aes(x = name, y = 100*fraction, fill = class2,
                                                     colour = class2)) +
    geom_bar(stat="identity", position="dodge") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    ggtitle("SH-SY5Y") +
    xlab("") +
    ggeasy::easy_add_legend_title("") 
p2_shsy | p2_patient

@@

ggplot(df2 %>%
           filter(type == "Patient"), aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("") |
    ggplot(df2 %>%
           filter(type != "Patient"), aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("")

>>>>

rel_rna_cryptic_amount %>%
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "UNC13A",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) +
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("UNC13A") +
    xlab("") +
    theme(legend.position = "none") +
    guides(color = FALSE) +
    theme(text = element_text(size = 20,family = 'sans'),
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28)) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(data = text_table[gene_name == "UNC13A"],aes(x = source, y= 1.35,label = padj_plot),size = 8) +
    geom_text(data = text_table[gene_name == "UNC13A"],aes(x = source, y= 1.2,label = log2FoldChange_plot),size = 8)
```

@@

rel_rna_cryptic_amount %>%
  left_join(text_table[,.(plot_name,source)]) %>% 
  unique() %>% 
  mutate(plot_name = fct_relevel(plot_name,"iPSC MN","SH-SY5Y","I3 Neurons","SK-N-DZ_a")) %>% 
    ggbarplot(,
              x = "plot_name",
              add = c("mean_se","jitter"),
              y = "TARDBP",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) +
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) +
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("TARDBP") +
    xlab("") +
    theme(legend.position = "none") +
    guides(color = FALSE) +
    theme(text = element_text(size = 20,family = 'sans'),
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28)) +
    scale_y_continuous(labels = scales::percent,expand = expansion(mult = c(0, .1))) +
    geom_text(data = text_table[gene_name == "TARDBP"],aes(x = plot_name, y= 1.35,label = padj_plot),size = 8) +
    geom_text(data = text_table[gene_name == "TARDBP"],aes(x = plot_name, y= 1.2,label = log2FoldChange_plot),size = 8)

@@

```{r}
force_colors = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
names(force_colors) = c("Control","ALS \n non-TDP","ALS-TDP","FTLD \n non-TDP","FTLD-TDP")
clean_data_table = fread(file.path(here::here(),"data","nygc_junction_information.csv"))
clean_data_table = clean_data_table %>%
    mutate(rs12973192 = fct_relevel(rs12973192,
                                    "C/C", "C/G", "G/G")) %>%
    mutate(number_g_alleles = as.numeric(rs12973192) - 1) %>%
    mutate(unc13a_cryptic_leaf_psi = ifelse(is.na(unc13a_cryptic_leaf_psi),0,unc13a_cryptic_leaf_psi)) %>%
    mutate(junction_reads_stmn2 = STMN2_annotated_leaf + STMN2_cryptic_leaf) %>%
    mutate(junction_reads_unc13a = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf + UNC13A_annotated_leaf) %>%
    unique()

@@

@@

unc13a_sequencing_platform_pct %>%
  ggplot(aes(x = plot_name, y = detection )) + 
  geom_col(fill = "firebrick") +
  labs(title = "UNC13A CE detection and sequencing platform", 
       y = "UNC13A CE detected",x = element_blank(), subtitle = "Fisher exact test") + 
  facet_wrap(~disease_group2 + tissue_clean,scales = 'free_x') +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_text(aes(x = 1.5, y = 1.05, label = paste0("p = ", signif(fisher_pvalue,digits = 2) ) )) +
  theme(legend.text = element_text(size = 15)) +
  ggpubr::theme_pubr() +
  scale_fill_manual(values = ("#b3251f"))
 # scale_y_continuous(expand = c(0,0) ) 
```

## Sequencing platform and disease type

Were there systemic differences in sequence platform between ALS and FTD?

```{r platform_compare}
tmp = clean_data_table %>%
  filter(tissue_clean %in% c("Frontal_Cortex", 
                             "Lumbar_Spinal_Cord", 
                             "Cervical_Spinal_Cord", 
                             "Motor_Cortex", 
                             "Temporal_Cortex")) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  mutate(tissue = as.character(tissue)) %>%
  filter(sequencing_platform != "") %>% 
  filter(disease_group2 %in% c("ALS-TDP","FTLD-TDP")) %>% 
  dplyr::select(tissue_clean,disease_group2,sequencing_platform) %>% 
  group_by(tissue_clean) %>% 
  nest()

tmp %>% 
  mutate(chisq_res = map(data, ~ .x %>% table() %>% chisq.test() %>% pluck('residuals')))
```

## Library size by disease status and tissue

```{r unc detection by library size  }
# library size

@@

## Effect of library depth on CE discovery

```{r unc detection by library depth}

unc13a_library_depth <- clean_data_table %>%
  filter(tissue_clean %in% c("Frontal_Cortex", 
                             "Lumbar_Spinal_Cord", 
                             "Cervical_Spinal_Cord", 
                             "Motor_Cortex", 
                             "Temporal_Cortex")) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  filter(disease_group2 %in% c("ALS-TDP","FTLD-TDP"))

unc13a_library_depth %>%
  group_by(disease_group2,tissue_clean) %>% 
  add_count() %>% 
  mutate(plot_name = glue::glue("{tissue_clean} \n {n}")) %>% 
  ggplot(aes(x = unc13a_detected, y = log10(library_size))) + 
  geom_boxplot(aes(fill = unc13a_detected), colour = "black", outlier.colour = NA) + 
  facet_wrap(~disease_group2+ plot_name) + 
  geom_jitter(height = 0,size = 2,alpha = 0.3) + 
  ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center", method = "wilcox", label.y.npc = 0.95) + 
  ggpubr::theme_pubr() +
  xlab("UNC13A CE Detected") + 
  scale_fill_manual(values = c("#EBC3B9","#b3251f")) + 
  theme(legend.position = 'none')
```

## RIN between cases and controls

```{r rin_cases_controls}
force_colors = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")
names(force_colors) = c("Control","ALS \n non-TDP","ALS-TDP","FTLD \n non-TDP","FTLD-TDP")

@@

## RIN and detection in cases
```{r rin_detection_cases}

unc13a_rin <- clean_data_table %>%
  filter(tissue_clean %in% c("Frontal_Cortex", 
                             "Lumbar_Spinal_Cord", 
                             "Cervical_Spinal_Cord", 
                             "Motor_Cortex", 
                             "Temporal_Cortex")) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  filter(disease_group2 %in% c("ALS-TDP","FTLD-TDP")) %>% 
  filter(rin != "")

unc13a_rin %>%
  group_by(disease_group2,tissue_clean) %>% 
  add_count() %>% 
  mutate(plot_name = glue::glue("{tissue_clean} \n {n}")) %>% 
  ggplot(aes(x = unc13a_detected, y = rin)) + 
  geom_boxplot(aes(fill = unc13a_detected), colour = "black", outlier.colour = NA) + 
  facet_wrap(~disease_group2+ plot_name) + 
  ylab("RIN") +
  geom_jitter(height = 0,size = 2,alpha = 0.3) + 
  ggpubr::stat_compare_means(label = "p.format", label.x.npc = "center", method = "wilcox", label.y.npc = 0.95) + 
  ggpubr::theme_pubr() +
  xlab("UNC13A CE Detected") +
  scale_fill_manual(values = c("#EBC3B9","#b3251f")) + 
  theme(legend.position = 'none')
```

@@

cell_types %>% 
  left_join(clean_data_table[,.(sample,
                               UNC13A_3prime_leaf,
                               UNC13A_5prime_1_leaf,
                               disease_group2,
                               disease_tissue)], by = 'sample') %>%
  filter(tissue_clean %in% c("Frontal_Cortex", 
                             "Lumbar_Spinal_Cord", 
                             "Cervical_Spinal_Cord", 
                             "Motor_Cortex", 
                             "Temporal_Cortex")) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  filter(disease_group2 %in% c("ALS-TDP","FTLD-TDP")) %>% 
  group_by(disease_group2,tissue_clean) %>% 
  add_count() %>% 
  mutate(n = n / 5) %>% 
  mutate(plot_name = glue::glue("{tissue_clean} \n {n}")) %>% 
  filter(!is.na(inclusion_reads)) %>% 
  unique() %>% 
  ggplot(aes(x = cell, y = deconv, fill = unc13a_detected)) + 
  # geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+
  geom_boxplot(outlier.color = NA) + 
  facet_wrap(~disease_group2+plot_name,scales = 'free') +
  ggpubr::stat_compare_means(label = "p.format",vjust = 1.3) +
  ggpubr::theme_pubr() +
  scale_fill_manual(values = c("#EBC3B9","#b3251f")) + 
  theme(legend.position = 'none') +
  xlab(element_blank())

@@

## UNC13A and UNC13B Intron Retention in NYGC

```{r unc13a_ir_in_newyork}
stat_test_a = clean_data_table %>% 
    filter(tissue_clean %in% c("Frontal_Cortex", 
                               "Lumbar_Spinal_Cord", 
                               "Cervical_Spinal_Cord", 
                               "Motor_Cortex", 
                               "Temporal_Cortex")) %>% 
    unique() %>% 
    group_by(tissue_clean) %>% 
    wilcox_test(IRratioUNC13A ~ disease_group2) %>%
    add_significance("p")

stat_test_b = clean_data_table %>% 
    filter(tissue_clean %in% c("Frontal_Cortex", 
                               "Lumbar_Spinal_Cord", 
                               "Cervical_Spinal_Cord", 
                               "Motor_Cortex", 
                               "Temporal_Cortex")) %>% 
    unique() %>% 
    group_by(tissue_clean) %>% 
    wilcox_test(IRratioUNC13B ~ disease_group2) %>%
    add_significance("p")

clean_data_table %>% 
    filter(tissue_clean %in% c("Frontal_Cortex", 
                               "Lumbar_Spinal_Cord", 
                               "Cervical_Spinal_Cord", 
                               "Motor_Cortex", 
                               "Temporal_Cortex")) %>% 
    unique() %>% 
    mutate(disease_group2 = fct_relevel(disease_group2, "Control")) %>% 
    ggplot(aes(x = disease_group2,
               y = IRratioUNC13A)) +
    geom_boxplot(aes(fill = disease_group2)) + 
    facet_wrap(~tissue_clean,scales = 'free_x') +
    stat_pvalue_manual(stat_test_a %>% filter(group1 == "Control" & group2 == "FTLD-TDP"), 
                       label = "p.signif",y.position = 0.98) +
    stat_pvalue_manual(
                       stat_test_a %>% filter(group1 == "ALS-TDP" & group2 == "Control"), 
                       label = "p.signif",y.position = 0.88) +
    ylab("UNC13A IRratio") +
  xlab(element_blank())+
  scale_fill_manual(values = force_colors) +
  ggpubr::theme_pubr() + 
  theme(legend.position = 'none')

```{r unc13b_ir_in_newyork}
clean_data_table %>% 
    filter(tissue_clean %in% c("Frontal_Cortex", 
                               "Lumbar_Spinal_Cord", 
                               "Cervical_Spinal_Cord", 
                               "Motor_Cortex", 
                               "Temporal_Cortex")) %>% 
    unique() %>% 
    mutate(disease_group2 = fct_relevel(disease_group2, "Control")) %>% 
    ggplot(aes(x = disease_group2,
               y = IRratioUNC13B)) +
    geom_boxplot(aes(fill = disease_group2)) + 
    facet_wrap(~tissue_clean,scales = 'free_x') +
    stat_pvalue_manual(stat_test_b %>% filter(group1 == "Control" & group2 == "FTLD-TDP"), 
                       label = "p.signif",y.position = 0.98) +
    stat_pvalue_manual(
        stat_test_b %>% filter(group1 == "ALS-TDP" & group2 == "Control"), 
        label = "p.signif",y.position = 0.88) +
    ylab("UNC13B IRratio") +
    scale_fill_manual(values = force_colors) +
    ggpubr::theme_pubr() + 
    theme(legend.position = 'none')

@@

```{r}
clean_data_table %>%
  filter(disease_tissue == T) %>%
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>%
  filter(junction_reads_stmn2 >= 30) %>%
  filter(junction_reads_unc13a >= 30) %>%
  # filter(UNC13A_3prime_leaf + UNC13A_5prime_1_leaf >= 2) %>%
  # filter(STMN2_cryptic_leaf >= 2) %>%
  filter(grepl("Cortex",tissue_clean)) %>%
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>%
  filter(unc13a_cryptic_leaf_psi > 0) %>%
  ggplot(aes(x = stmn_2_cryptic_psi_leaf, y = unc13a_cryptic_leaf_psi)) +
  geom_point(pch = 21, size = 3) +
  stat_cor(size = 8,method = "spearman",cor.coef.name = "rho") +
  geom_smooth(method = lm, se = FALSE,color = "black") +
  xlab("STMN2 Cryptic PSI") +
  ylab("UNC13A CE PSI") +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 18)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1L))  +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1L)) 
```
## Scatter plot showing the correlation in non-log space RAP1GAP1 & STMN2 CE

@@

```
## Detection by genotype
```{r}

clean_data_table %>%
  filter(!(rs12973192 == "C/G" & rs12608932 == "C/C")) %>%
  mutate(snp_status = case_when(rs12973192 == "C/C" ~ "healthy/healthy",
                                rs12973192 == "C/G" ~ "healthy/risk",
                                rs12973192 == "G/G" ~ "risk/risk")) %>% 
  filter(disease_tissue == T) %>%
  filter(junction_reads_stmn2 >= 30) %>%
  filter(junction_reads_unc13a >= 30) %>%

@@

overall_fisher %>%
  mutate(n_sample = n_non_detected + n_sample_detected) %>%
  mutate(detection_rate = n_sample_detected / n_sample) %>%
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>%
  ggplot(aes(x = detection_name, y = detection_rate, fill = detection_name)) +
  geom_col(show.legend = F) +
  ggpubr::theme_pubr() +
  scale_y_continuous(labels = scales::percent) +
  ylab("% of TDP-43 Proteionopathy Patients \n UNC13A Cryptic Detected") +
  theme(text = element_text(size = 18)) +
  xlab("N individuals") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggtitle(label = "ALS/FTD-TDP patients",subtitle =  glue::glue("Chi-squared Test: p-value {round(over_p,2)}"))

@@

cowplot::plot_grid(rap1_fold_plot,pfkp_fold_plot)
```

# Nanopore

@@

ggplot(df %>% filter(classification != "",
                                type=="SHSY5Y"), aes(x = name, y = fraction, fill = class2,
                                                     colour = class2)) +
    geom_bar(stat="identity", position="dodge") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    ggtitle("SH-SY5Y") +
    xlab("") +
    ggeasy::easy_add_legend_title("") +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1L))

@@

ggplot(df2 %>%
           filter(type == "Patient"), aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("")

    ggplot(df2 %>%
           filter(type != "Patient"), aes(x = name, y = 100*f, fill = classification)) +
    geom_bar(stat="identity") +
    ggpubr::theme_pubr() +
    ggeasy::easy_rotate_x_labels(side = "right") +
    ylab("Percentage of reads") +
    xlab("") +
    ggeasy::easy_add_legend_title("")
